Title: A proof-of-concept study

### 2022-01-06 paper.tex
update

\documentclass[twocolumn]{aastex631}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{txfonts}
\usepackage{lipsum, babel}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{xcolor,colortbl}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{url}
\usepackage{subfigure}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{empheq}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{mathrsfs}
\usepackage{soul}
\pdfminorversion=5

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{Comparison of the cases with (left) and without (right) the dense disk.\
             In the both cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
             with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through the jet source show that the dense disk not only helps the bubbles to align the disk normal\
             but also create an under pressure, cold, and dense bubble in the most inner region.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

@@

  \begin{figure*}
    \includegraphics[width=\linewidth]{figures/fig__xRay.png}
    \caption{One-dimensional surface-brightness\
             profiles in the same energy band\
             , cut at various galactic latitudes (as labelled).\
             For comparison, we also show ...}
    \label{fig__xRay.png}
  \end{figure*}

>>>>

\documentclass[twocolumn]{aastex631}
\usepackage{mathtools}
\usepackage{natbib}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={(},close={)}}
\usepackage{txfonts}
\usepackage{lipsum, babel}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{xcolor,colortbl}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{url}
\usepackage{floatrow}
%\usepackage[FIGTOPCAP]{subfigure}
\usepackage{subfigure}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cleveref}
\usepackage{physics}
\usepackage{empheq}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\usepackage{multirow}
\usepackage[flushleft]{threeparttable}
\usepackage{mathrsfs}
\usepackage{soul}
\pdfminorversion=5

@@

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp.png}
    \caption{Comparison of the cases with (left) and without (right) the dense disk.\
             In the both cases, the bipolar jets are injected at the origin along the $z=-y$ direction\
             with a constant 4-velocity of 0.6 for a duration of 1.2 Myr.
             The pressure (top), temperature (middle), and number density (bottom) slices\
             through the jet sources show that the dense disk not only helps the bubbles to align the disk normal\
             but also creates an under pressure, cold, and dense bubble in the most inner region.
             }
    \label{fig__jetI5+ismSeed3-45deg_no-disk-stratified-ambient-Pres-Dens-Temp}
  \end{figure}

@@

  %\begin{figure*}[ht]
  \begin{figure*}
    \subfigure[Simulated count rate (photons s$^{-1}$ deg$^{-2}$) map in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection.]
     {
      \includegraphics[width=\linewidth]{figures/fig__xray_0.8keV_angle_000.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__x-ray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{dddd}
    \label{fig_xray}
  \end{figure*}
